---
title: "Ex: Capital Market"
author: "Yiqiao Yin"
date: "Febuary 4, 2019"
output:
  rmdformats::readthedown: 
    toc: 1
  #html_document:
  #  theme: sandstone
  #  highlight: tango
  #prettydoc::html_pretty: # Source: https://cloud.r-project.org/web/packages/prettydoc/vignettes/architect.html
  #  theme: tactile # Selection: cayman, tactile, architect, leonids, hpstr
  #  highlight: vignette # Selection: github, vignette
  #  toc: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=12) 
```

# Brief

This RMD file is prepared for homework assignment for a class. I will introduce the situation, the goal, and audience to make the story vivid for my reader.

<a href="#top">Back to top</a>

# Story

Here is the situation:

- **background**: I am a research analyst that works for a Research Department at a trading firm; 

- **task**: my job is to provide an overview of a few stocks for traders to look at (say this time it's the Tech Sector); 

- **goal**: the following presentation consists of two plots and the presentation aims to give audience (i.e. traders) an overview of the big tech firms about (1) returns, (2) cumulative values, (3) portfolio components, etc..

<a href="#top">Back to top</a>

# Presentation

In this presentation, we present two parts: 

- **Overview**

- **Performance Comparison**

## Overview

Overview of stock charts (in format of candlesticks). This following plot gives traders an overview of the path for top 4 companies in Technology Sector. Traders can use this presentation as layout and it is apparent that Apple took a relatively bigger hit than the other three in the past year.

```{r, message=FALSE, error=FALSE, warning=FALSE, echo=FALSE}
# Initiate Library
library(quantmod)
library(ggplot2)
library(tidyverse)
library(tidyquant)
library(gridExtra)
library(grid)

# Download Data
# Use FANG data set
data("FANG")

# Get AAPL and AMZN Stock Prices
# to = "2018-12-31"
AAPL <- tq_get("AAPL", get = "stock.prices", from = "2016-01-01")
AMZN <- tq_get("AMZN", get = "stock.prices", from = "2016-01-01")
GOOGL <- tq_get("GOOGL", get = "stock.prices", from = "2016-01-01")
MSFT <- tq_get("MSFT", get = "stock.prices", from = "2016-01-01")

# Overview
overview.1 <- AAPL %>%
    ggplot(aes(x = date, y = close)) + 
    geom_candlestick(aes(open = open, high = high, low = low, close = close)) + 
    labs(title = "AAPL Candlestick Chart", y = "Closing Price", x = "") + 
    geom_ma(ma_fun = SMA, n = 50, color = "blue", linetype = 5, size = 0.5) + 
    geom_ma(ma_fun = SMA, n = 200, color = "purple", linetype = 5, size = 0.5) + 
    theme_tq()
overview.2 <- AMZN %>%
    ggplot(aes(x = date, y = close)) +
    geom_candlestick(aes(open = open, high = high, low = low, close = close)) +
    labs(title = "AMZN Candlestick Chart", y = "Closing Price", x = "") +
    geom_ma(ma_fun = SMA, n = 50, color = "blue", linetype = 5, size = 0.5) + 
    geom_ma(ma_fun = SMA, n = 200, color = "purple", linetype = 5, size = 0.5) + 
    theme_tq()
overview.3 <- GOOGL %>%
    ggplot(aes(x = date, y = close)) +
    geom_candlestick(aes(open = open, high = high, low = low, close = close)) +
    labs(title = "GOOGL Candlestick Chart", y = "Closing Price", x = "") +
    geom_ma(ma_fun = SMA, n = 50, color = "blue", linetype = 5, size = 0.5) + 
    geom_ma(ma_fun = SMA, n = 200, color = "purple", linetype = 5, size = 0.5) + 
    theme_tq()
overview.4 <- MSFT %>%
    ggplot(aes(x = date, y = close)) +
    geom_candlestick(aes(open = open, high = high, low = low, close = close)) +
    labs(title = "MSFT Candlestick Chart", y = "Closing Price", x = "") +
    geom_ma(ma_fun = SMA, n = 50, color = "blue", linetype = 5, size = 0.5) + 
    geom_ma(ma_fun = SMA, n = 200, color = "purple", linetype = 5, size = 0.5) + 
    theme_tq()

# Scatterplot
grid.arrange(
  overview.1, 
  overview.2, 
  overview.3, 
  overview.4, nrow = 2)
```

 <a href="#top">Back to top</a>

## Performance Comparison

We download the stocks that are big four large cap stocks in Tech Sector (AAPL, AMZN, GOOGL, and MSFT). The graphs illustrates 

- **top-left**: The paths of returns for individual stocks plotted together since 2016. The x-axis is time and the y-axis is returns.

- **top-right**: The paths of dollar values for $\$100$ dollars invested in each individual stock plotted together since 2016. The x-axis is time and the y-axis is values.

- **bottom-left**: Multiple plots from Modern Portfolio Theorey (MPT). The x-axis is risk (measured by standard deviation of returns) and the y-axis is reward (measured by expectation of returns). The black dots are all the single assets. The blue curvatures coonect only two assets. The black dotted line is the efficient frontier (constructed by drawing a line that just covers all the double-asset portfolios). The purple line is the market capital line, drawn by looking at the tangent of the efficient frontier and the risk-free asset. The tangent portfolio (also known as efficient portfolio) has the smallest risk with the highest reward and this portfolio actually holds weights (28\% for Apple, 42\% for Google, and 29\% for Microsoft).

- **bottom-right**: The plot presents four paths while each path is for a particular performance measured in returns for a certain time unit. These time units are weekly, monthly, quarterly, and yearly. The x-axis is the indicator for individual stocks. They are the four stocks in this report, AAPL, AMZN, GOOGL, and MSFT.

- **interesting phenomenon**: Modern Portfolio Theory actually suggests to hold Apple even though in the Overview it seemed that Apple has dropped the most.

```{r, message=FALSE, error=FALSE, warning=FALSE, echo=FALSE}
# 3D Plot
All.Indice.3D <- function() {
  data <- getSymbols(c(
    "AAPL", "AMZN", "GOOGL", "MSFT"
  )); data
  data.list <- list(
    AAPL, AMZN, GOOGL, MSFT
  )
  
  # Create data set:
  all <- matrix(NA,nrow=length(data),ncol=12)
  rownames(all) <- data
  
  # Update Price (Current, daily basis):
  for (i in c(1:nrow(all))){
    all[i,2] <- data.frame(data.list[i])[nrow(data.frame(data.list[i])),4]
  }
  
  # Update Momentum:
  for (i in c(1:nrow(all))){
    all[i,5] <- (data.frame(data.list[i])[nrow(data.frame(data.list[i])),4])/(data.frame(data.list[i])[(nrow(data.frame(data.list[i]))-5),4])-1
  }
  for (i in c(1:nrow(all))){
    all[i,6] <- (data.frame(data.list[i])[nrow(data.frame(data.list[i])),4])/(data.frame(data.list[i])[(nrow(data.frame(data.list[i]))-25),4])-1
  }
  for (i in c(1:nrow(all))){
    all[i,7] <- (data.frame(data.list[i])[nrow(data.frame(data.list[i])),4])/(data.frame(data.list[i])[(nrow(data.frame(data.list[i]))-25*3),4])-1
  }
  for (i in c(1:nrow(all))){
    all[i,8] <- (data.frame(data.list[i])[nrow(data.frame(data.list[i])),4])/(data.frame(data.list[i])[(nrow(data.frame(data.list[i]))-252),4])-1
  }
  
  # Clearn up
  all <- all[,-c(1,3,4,9,10,11,12)]
  
  # Update column names:
  colnames(all) <- c("Last Price",
                     "Pre 5-Days",
                     "Pre 30-Days", 
                     "Pre Quarter",
                     "Pre Year")
  
  # Quick vertical bar plot:
  counts <- all[,2]
  counts.std <- sd(all[,2])
  #barplot(counts, main="5-Day Return Bar Chart", #horiz=TRUE,
  #        names.arg=rownames(all), cex.names=0.35,
  #        col=ifelse(counts>counts.std,"green",ifelse(counts<(-1)*counts.std,"red","pink")))
  
  # Sortable table:
  library('DT')
  # Present table:
  d = data.frame(
    round(all[,c(2,3,4,5)],4),
    #round(all[,c(2,3,4,5)],4),
    stringsAsFactors = FALSE)
  #d <- data.frame(cbind(
  #  rownames(d),
  #  d
  #))
  #colnames(d)[1] <- "Name"
  
  # Output
  return(d)
} # End of function
```


```{r, message=FALSE, error=FALSE, warning=FALSE, echo=FALSE}
# Set
par(mfrow = c(2,2))

# --------------------------
# Return Comparisons
# --------------------------
library(quantmod)
tckrs <- c("AAPL", "AMZN", "GOOGL", "MSFT")
getSymbols(tckrs, from = "2016-01-01")
AAPL.Close <- AAPL[, 4];AMZN.Close <- AMZN[, 4];GOOGL.Close <- GOOGL[, 4];MSFT.Close <- MSFT[, 4]
AAPL1 <- as.numeric(AAPL.Close[1])
AMZN1 <- as.numeric(AMZN.Close[1])
GOOGL1 <- as.numeric(GOOGL.Close[1])
MSFT1 <- as.numeric(MSFT.Close[1])
AAPL.2 <- AAPL.Close/AAPL1-1; AMZN.2 <- AMZN.Close/AMZN1-1; GOOGL.2 <- GOOGL.Close/GOOGL1-1; MSFT.2 <- MSFT.Close/MSFT1-1
basket <- cbind(AAPL.2, AMZN.2, GOOGL.2, MSFT.2)
zoo.basket <- as.zoo(basket)

# Set a color scheme:
tsRainbow <- rainbow(ncol(zoo.basket))
# Plot the overlayed series
plot(x = zoo.basket, ylab = "Cumulative Return", 
     ylim = c(-0.5, 2.5), xlab = "Time", main = "Cumulative Returns (Percentage Growth in Individual Stocks)", col = tsRainbow, screens = 1)
# Set a legend in the upper left hand corner to match color to return series
legend(x = "topleft", legend = c("AAPL", "AMZN", "GOOGL", "MSFT"), lty = 1, col = tsRainbow)

# --------------------------
# Value Comparisons
# --------------------------
library(quantmod)
#tckrs <- c("AAPL", "AMZN", "GOOGL", "MSFT")
#getSymbols(tckrs, from = "2016-01-01")
AAPL.Close <- AAPL[, 4];AMZN.Close <- AMZN[, 4];GOOGL.Close <- GOOGL[, 4];MSFT.Close <- MSFT[, 4]
AAPL1 <- as.numeric(AAPL.Close[1])
AMZN1 <- as.numeric(AMZN.Close[1])
GOOGL1 <- as.numeric(GOOGL.Close[1])
MSFT1 <- as.numeric(MSFT.Close[1])
AAPL.3 <- AAPL.Close/AAPL1*100; AMZN.3 <- AMZN.Close/AMZN1*100; GOOGL.3 <- GOOGL.Close/GOOGL1*100; MSFT.3 <- MSFT.Close/MSFT1*100
basket <- cbind(AAPL.3, AMZN.3, GOOGL.3, MSFT.3)
zoo.basket <- as.zoo(basket)

# Set a color scheme:
tsRainbow <- rainbow(ncol(zoo.basket))
# Plot the overlayed series
plot(x = zoo.basket, ylab = "Value Comparison", 
     ylim = c(0, 350), xlab = "Time", main = "Cumulative Values ($100 Initial Investment in Individual Stocks)", col = tsRainbow, screens = 1)
# Set a legend in the upper left hand corner to match color to return series
legend(x = "topleft", legend = c("AAPL", "AMZN", "GOOGL", "MSFT"), lty = 1,col = tsRainbow)

# --------------------------
# Quant Plot
# --------------------------
# CAPM:
# load the data
library(data.table)
tickers <- c("AAPL", "AMZN", "GOOGL", "MSFT")
Start.Date <- "2010-01-01"; End.Date <- "2018-01-01"
#getSymbols(tickers)
closePrices <- do.call(merge, lapply(tickers, function(x) Cl(get(x))))
Stock.Return <- function(x) {diff(x)/lag(x)}
df <- data.table(Stock.Return(closePrices[,1]),
                 Stock.Return(closePrices[,2]),
                 Stock.Return(closePrices[,3]),
                 Stock.Return(closePrices[,4]) )
df <- na.omit(df)

# calculate the necessary values:
library(fPortfolio)

# I) expected returns for the two assets
return.matrix <- df
# II) risk (standard deviation) as a risk measure
df.vector <- apply(return.matrix, 2, sd)
# III) covariance
cov_matrix <- cov(df)

# Efficient Frontier
frontier=portfolioFrontier(as.timeSeries(return.matrix))
frontierPlot(frontier); grid()
minvariancePoints(frontier,col="red",pch=20)
cmlPoints(frontier,col="#f0f8ff",pch=20)
tangencyPoints(frontier,col="yellow",pch=4)
tangencyLines(frontier,col="#8a2be2",lwd=2)
twoAssetsLines(frontier,col="#40e0d0",lwd=2)
singleAssetPoints(frontier,col="black",pch=20)

# --------------------------
# Slider Matplot
# --------------------------
# Data
df <- data.frame(cbind(
  name = c("AAPL", "AMZN", "GOOGL", "MSFT"),
  All.Indice.3D()))
dat <- as.matrix(df[,-1]) # make data
# Create the data for the chart.
v <- dat[,1]
t <- dat[,2]
m <- dat[,3]
n <- dat[,4]

# Plot the bar chart.
plot(v, type = "o", xaxt = "n", col = 1, xlab = "Stocks", 
     ylab = "Value", main = "Previous W/M/Q/Y Returns",
     ylim = c(min(dat), max(dat)+0.2))
lines(t, type = "o", col = 2)
lines(m, type = "o", col = 3)
lines(n, type = "o", col = 4)
axis(1, at = 1:4, labels = c("AAPL", "AMZN", "GOOGL", "MSFT"), cex.axis = 0.7)
legend("topleft", legend = c("Past.Week.Return","Past.Month.Return",
                             "Past.Quarter.Return","Past.Year.Return"), col = 1:4, pch= 1)
```

<a href="#top">Back to top</a>

# Supplement

The supplement presents print-out of the weights of different portfolios.

```{r, message=FALSE, error=FALSE, warning=FALSE, echo=FALSE}
closePrices <- do.call(merge, lapply(tickers, function(x) Cl(get(x))))
dateWindow <- c(Start.Date, End.Date)
      
# CAPM:
# load the data
Stock.Return <- function(x) {
  diff(x)/lag(x)
}
df <- data.table(Stock.Return(closePrices[,1]),
                 Stock.Return(closePrices[,2]),
                 Stock.Return(closePrices[,3]),
                 Stock.Return(closePrices[,4])
)
df <- na.omit(df)

## Clean Data
# Load Data and Convert to timeSeries Object:
Data = as.timeSeries(df) #Data

## portfolioSpec ##
# Set Default Specifications:
Spec = portfolioSpec()
#Spec
setTargetReturn(Spec) = mean(colMeans(Data))

## Allow for unlimited Short Selling:
Constraints = "LongOnly"

## minvariancePortfolio ##
# Compute properties of minimum variance Portfolio:
Minimum.Risk.Money <- minvariancePortfolio(Data, Spec, Constraints); unlist(Minimum.Risk.Money)
```